% Source: https://github.com/sb2nov/resume
\input{header}

\begin{document}

%----------HEADING----------
\vspace*{-0.3cm}
\begin{center}
    {\color{primary-color}\Huge Nguyen Dinh Dang Khoa} \\[5mm]
    {\raisebox{-0.1\height}\faEnvelope\ nddkhoaa@gmail.com}
    \vspace{-8pt} ~~
    \href{https://facebook.com/nddkhoaaa}{\raisebox{-0.1\height}\faFacebook\ {Facebook}} ~~
    \href{https://github.com/balldk}{\raisebox{-0.1\height}\faGithub\ {github.com/balldk}} ~~
    \href{https://justkhoa.me/}{\raisebox{-0.1\height}\faGlobe\ {justkhoa.me}}
    \vspace{-8pt}
\end{center}
\vspace{1cm}
I am a sophomore in Mathematics, majoring in Algebra. Passionate about abstract maths, theoretical computer science, and cryptography. I have some experiences in software development, though I'm planning doing research in the future.
\vspace{-2mm}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{University of Science - VNUHCM}{Sept 2020 -- Present}
{Bachelor in Mathematics, majoring in Algebra.}{Ho Chi Minh city - Vietnam}\\
\item{\small\textbf{GPA:} 8.6$/$10.}

\resumeSubHeadingListEnd
\vspace{-4pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Seedcom}{Oct 2021 -- Present}
{Fullstack Developer of Coretech team}{Ho Chi Minh city -- Vietnam}
\resumeItemListStart
\resumeItem{Developed and maintain an analytics system based on Superset -- An open source project of Apache.}
\resumeItem{Technologies: Python, React.js, PostgreSQL, MySQL.}
\resumeItemListEnd

\resumeSubheading
{200Lab}{Aug 2020 -- Jan 2021}
{Backend Developer}{Ho Chi Minh city -- Vietnam}
\resumeItemListStart
\resumeItem{Developed and design some small CRUD modules on top of microservices architecture for\\a livestream app.}
\resumeItem{Technologies: Go, MySQL.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Side Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Justkhoa.me -- Personal blog}}{July 2021}
\resumeItemListStart
\resumeItem{A nice-looking personal blog built from scratch.}
\resumeItem{Support markdown, latex, auto generate TOC, comment section,...}
\resumeItem{Mostly write about my understandings in Math and Computer Science.}
\resumeItem{Technologies: Go, Nuxt.js, MySQL.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Tutorbot -- Online matching tutor app}}{March 2020}
\resumeItemListStart
\resumeItem{A Facebook Messenger Chatbot that connects students and tutors from different places together based on their age and learning purposes.}
\resumeItem{Attracted hundreds of users within first-month operation.}
\resumeItem{Technologies: Node.js, MongoDB, Messenger Platform.}
\resumeItemListEnd

\resumeProjectHeading
%   {\textbf{Gym Reservation Bot} $|$ \emph{Python, Selenium, Google Cloud Console}}{January 2021}
{\textbf{Bitexam -- Exam storage system}}{November 2018}
\resumeItemListStart
\resumeItem{A system built on top of Ethereum smart contract, aiming at large-scale exams which need high reliability.}
\resumeItem{Able to store examinees' tests securely, prevent some alternation factors.}
\resumeItem{Technologies: Solidity, Web3.js, Electron.js, Vue.js.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\pagebreak
%-----------SKILLS-----------
\section{Skills}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Mathematics:}}{}
\resumeItemListStart
\resumeItem{Undergraduate level of mathematical thinking.}
\resumeItem{Have a concrete understanding of some fundamental subjects such as Linear Algebra, Calculus, Analysis, Discrete Math.}
\resumeItem{Familiar with abstract spaces such as metric space, Hilbert space, topological space,...}
\resumeItem{Familiar with group, ring, field through Modern Algebra, Field and Galois Theory courses.}
\resumeItem{Able to use some math tools: Matlab, Mathematica, Julia, Coq.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Programming:}}{}
\resumeItemListStart
\resumeItem{\textbf{Familiar with: }Go, Python, Node.js, Vue.js, MySQL, Git, Blockchain, Matlab, Latex.}
\resumeItem{\textbf{Know$/$Used:} Docker, React.js, Julia, MongoDB, PostgreSQL.}
\resumeItem{\textbf{Hobby$/$Interested in:} Rust, Haskell.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Language:}}{}
\resumeItemListStart
\resumeItem{\textbf{Vietnamese: }Mother tongue.}
\resumeItem{\textbf{English: }Fluent.}
\resumeItem{\textbf{French: }Hobby.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS---------------
\section{Achievements}
\resumeSubHeadingListStart

\item{
            \resumeItemListStart
            \resumeItem{Ranked Third in Informatics at "HCMC Excellent Student Competition".\hfill \textbf{2019 -- 2020}}
            \resumeItem{Bronze Medal in Informatics at "HCMC April Olympic Competition".\hfill \textbf{2018 -- 2019}}
            \resumeItem{Gold Medal in Informatics at "HCMC April Olympic Competition".\hfill \textbf{2017 -- 2018}}
            \resumeItemListEnd
      }

\resumeSubHeadingListEnd

\end{document}
